%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj + some brand new features from Mary Feofanova
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{makecell}
\usepackage[link=off]{phonenumbers}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage[margin=0.3in]{geometry}
% Adjust margins
\addtolength{\oddsidemargin}{-0.0in}
\addtolength{\evensidemargin}{-0.0in}
\addtolength{\textwidth}{0in}
\addtolength{\topmargin}{20pt}
\addtolength{\textheight}{0.0in}

\urlstyle{same}

\usepackage{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{hyperref}% http://ctan.org/pkg/hyperref
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  linkbordercolor=red,
  urlcolor=blue!70!black
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\def \ifempty#1{\def\temp{#1} \ifx\temp\empty }

\newcommand{\resumeItem}[2]{
  \item\small{
  	\ifempty{#1}#2\else\textbf{#1}{: #2 \vspace{-2pt}}\fi
  }
}

\usepackage[dvipsnames]{xcolor}
\definecolor{mygray}{gray}{0}
\usepackage{fancybox}

\usepackage{lmodern}
\usepackage{tikz}

% Style definition
\tikzset{rndblock/.style={rounded corners,rectangle,draw,outer sep=0pt}}

% Command Definition
% 1 optional to customize the aspect, 2 mandatory: text to be framed
\newcommand{\tframed}[2][]{\tikz[baseline=(h.base)]\node[rndblock,#1] (h) {\color{black}{#2}};}

\newcommand*{\mystrut}{\rule[-0.2\baselineskip]{0pt}{0.8\baselineskip}}
\newcommand{\skill}[1]{\tframed[lightgray]{\mystrut#1}}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeExpSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
      {\scriptsize#5}
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeProjSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \scriptsize {#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{changepage}
\newcommand{\resumeDesc}[1]{\begin{adjustwidth}{5pt}{0pt}\vspace{-2pt}{\small{#1}}\end{adjustwidth}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Mariia (Mary) Feofanova} & Email : \href{mailto:mary.fifa3000@gmail.com}{mary.fifa3000@gmail.com}\\
  Github: \href{https://github.com/mary3000}{mary3000} & Mobile : +7\hspace{0.5ex}916\hspace{0.5ex}835\hspace{0.5ex}49\hspace{0.5ex}66 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
       {Moscow Institute of Physics and Technology [planned]}{Moscow, Russia}
      {Master's degree in Computer Science}{Sept. 2020 - Aug. 2022}
  \resumeSubheading
       {The Yandex School of Data Analysis}{Moscow, Russia}{Big Data Infrastructure}{Sept. 2019 - Aug. 2022 (Present)}
    \resumeSubheading
      {Moscow Institute of Physics and Technology}{Moscow, Russia}
      {Bachelor of Applied Mathematics 
       and Computer Science}{Sept. 2016 - Aug. 2020 (Present)}
	 %\begin{comment}
	 \resumeItemListStart
        \resumeItem{Thesis}
          {Verification of synchronization primitives and concurrent data structures}
      \resumeItemListEnd
      %\end{comment}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeExpSubheading
      {JetBrains}{St. Petersburg, Russia (remote)}
      {Research Intern, Programming Languages and Tools Lab}{July 2020 - Aug. 2020}
      {\skill{C} \skill{LLVM}}
      \resumeDesc{
      \begin{itemize}
          \item Verifying concurrent C programs under weak memory model with \href{https://plv.mpi-sws.org/genmc/}{GenMC} model checker.
      \end{itemize}}
      \resumeExpSubheading
      {Google}{London, UK}
      {SWE Intern, Android App Compat team}{July 2019 - Sept. 2019}
      {\skill{GoLang} \skill{Java} \skill{Android} \skill{C++} \skill{Protobuf} \skill{SQL}}
      \resumeDesc{
      \begin{itemize}
          \item Analyzed statistics about Android API usage and wrote design document about its utilization.
          \item Integrated statistics into Android source code presubmit checker: now it warns if pull-request changes will break popular apps.
      \end{itemize}}
      \resumeExpSubheading
      {Moscow Institute of Physics and Technology}{Moscow, Russia}
      {Teaching Assistant, "Theory and Practice of Concurrent Computing" course}{Feb. 2019 - Present}
      {\skill{C++} \skill{x86 Assembly}}
      \resumeDesc{
      \begin{itemize}
          \item Holding seminars, reviewing homework, improving test infrastructure.
      \end{itemize}
      }
      \resumeExpSubheading
      {JetBrains}{Moscow, Russia}
      {\makecell[l]{SWE, RubyMine team \\ SWE Intern, RubyMine team}}{\makecell[r]{Oct. 2018 - Feb. 2019 \\ Jul. 2018 - Aug. 2018}}
      {\skill{Java} \skill{Ruby} \skill{Ruby on Rails}}
      \resumeDesc{\begin{itemize}
          \item Developed new intentions, inspections and refactoring options (e.g. \href{https://www.jetbrains.com/help/ruby/introduce-parameter.html}{introduce parameter}) for RubyMine IDE. 
          \item Improved Rails-specific refactoring system: model fields, associations support.
      \end{itemize}}
       
    
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
  
      \resumeProjSubheading
      {\href{https://gitlab.com/mary3000/twist/-/tree/model-checker-merge/twist/checker}{Model checker for concurrent programs} [Bachelor thesis]}{Moscow, Russia}
      {\skill{C++}}{Nov. 2019 - May 2020}
          \resumeDesc{Wrote model checker that tests concurrent C++ programs. Key feature: code doesn't need to be translated to formal language (like TLA+ / +Cal). Verified my work on non-trivial examples: ABA bug inside lock-free cache for Yandex allocator (finds bug 16 times faster than +Cal) and bug inside implementation of Executors framework.}
  
    \resumeProjSubheading
      {\href{https://github.com/QratorLabs/inclickdb}{InclickDB}}{Moscow, Russia}
      {\skill{GoLang} \skill{Python} \skill{Grafana} \skill{Graphite} \skill{ClickHouse} \skill{InfluxDB}}{May 2019}
          \resumeDesc{Investigated possible solutions to a problem of migrating from InclickDB to ClickHouse for a monitoring system with tagged metrics. Created tag support in existing solution by teaching myself Golang and contributed to open-source: \href{https://github.com/lomik/carbon-clickhouse/pull/32}{pull-request}.}
          
    \begin{comment}  
    \resumeProjSubheading
      {\href{https://github.com/AndroidTopTeam/MyChief}{MyChief}}{Moscow, Russia}
      {\skill{Java} \skill{Android}}{Nov. 2017}
      \resumeDesc{Learned Android and implemented all structure and internal code logic (activities, fragments, lru cache) of mobile app that can search for recipes with ingredients entered by user, collaborated with a team of 3 students.}
    \end{comment}
      
  \resumeSubHeadingListEnd

\section{Achievements}
  \resumeSubHeadingListStart
    \resumeProjSubheading
      {\href{https://github.com/PhotoLabBestTeam/heroku}{Photo Lab Live Challenge: Go Viral or Go Home} - I place [Hackathon]}{Moscow, Russia}
      {\skill{Python} \skill{web.py} \skill{Heroku}}
      {Nov. 2018}
          \resumeDesc{Developed backend for photo filter that changes clothes style, having only 48 hours was able to quickly learn python framework and to deploy MVP.}
  \resumeSubHeadingListEnd
%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: C++, GoLang, Java, Python, TLA+, +Cal. }
   }\vspace{-7pt}
   \item{
     \textbf{Technologies}{: SQL, Git, \LaTeX, Docker. }
   }
   \vspace{-7pt}
   \item{
     \textbf{Knowledge}{: Algorithms, Data Structures, Concurrent Computing, Distributed Systems.}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
